DATA 621 Homework #4

### 2019-11-09 hw4/HW4.Rmd
Added baseline model

>>>>

## Model Creation

### Baseline Model

```{r}
evaluate_model <- function(model, test_df){
  test_df$yhat <- ifelse(predict.glm(model, test_df,"response") >= 0.5, 1, 0)
  cm <- confusionMatrix(factor(test_df$yhat), factor(test$TARGET_FLAG), "1")
  deviance <- model$deviance
  r2 <- 1 - model$deviance / model$null.deviance

  cat("F1 =", cm$byClass[7],"\nR2 =", r2, "\n\n")
  print(cm)
  return(cm)
}
```

We will create a simple model to serve as the baseline.  This model posits that drivers history is a good representation of their future.  So drivers that have been in an accident (`OLDCLAIM` > 0 or `AVG_CLAIM` > 0) are more likely to be in an accident.  Conversely those who haven't aren't likely to be in one in the future.

```{r, null_prefix = TRUE, comment=NA}
baseline_model <- over_sample_train %>%
  mutate(PRIOR_ACCIDENT = ifelse(OLDCLAIM == 0 & AVG_CLAIM == 0, 0, 1)) %>%
  glm(TARGET_FLAG ~ PRIOR_ACCIDENT, family = binomial(link = "logit"), .)
summary(baseline_model)

results <- test %>%
  mutate(PRIOR_ACCIDENT = ifelse(OLDCLAIM == 0 & AVG_CLAIM == 0, 0, 1)) %>%
  evaluate_model(baseline_model, .)
```

This simple model has statistically significant predictors.  Applying this model to the test data set indicates this simple model has a `r  round(unname(results$overall['Accuracy'])*100,1)`% accuracy rate.  It correcly identified `r round(unname(results$byClass['Sensitivity'])*100,1)`% of the people with accidents and `r  round(unname(results$byClass['Specificity'])*100,1)`% of those without.  It is better than flipping a coin but not by much.  All future models must outpreform this baseline.
